Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-10 arxiv/setup.tex

\paragraph{Notations.}
Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.

>>>>

\paragraph{Notations.}
Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
